\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-19 paper.tex
Extended intro

As Bitcoin's economic presence grows, formal specifications, abstracted away from current current implementations of the Bitcoin protocol, will become increasingly essential in mediating conflict over what Bitcoin is or should be, allowing participants in the Bitcoin community to reason formally and precisely about their opinions and proposals.

\textcolor{blue}{[Describe history of Script and Bitcoin maybe, say the language was flawed]}

\textcolor{blue}{[Mention [3] when it says that "These limitations are encoded in a function called isStandard(), which defines five types of "standard" transactions. These limitations are temporary and might be lifted by the time you read this."
The transaction programs being subject to change justifies allowing formal reasoning about the language.]}

>>>>

To prevent attacks on the Bitcoin network based on exploiting a flaw in Script, the Bitcoin community agreed on a set of ``standard'' script templates that nodes will process. These limitations, however, are deemed temporary and subject to change in the future [3], although no consensus exists at the moment on what should replace these limitations, if anything. As Bitcoin's economic presence grows, formal specifications, abstracted away from current implementations of the Bitcoin protocol, will become increasingly essential in mediating conflict over what Bitcoin is or should be, allowing participants in the Bitcoin community to reason formally and precisely about their opinions and proposals.

\textcolor{blue}{[anything else? can we add more examples of how a lack of formal specification was problematic?]}
